Title for Super Fancy Stuff

### 2025-04-30 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, important fixes
>w<, changes

            % =======================

@@

            % ==============================

@@

            Let $\bar v = (\bar y, \bar x_1, \bar x_2, \xi) \in \RR^m\times \RR^{n_1} \times \RR^{n_2}\times \RR$ then the right multiplication of has: 
            \begin{align*}
                \bar v^TA  &= (
                    E_1^T\bar y + \xi c_1^T,\; E_2^T\bar y + \xi c_2^T,\; 
                    \bar x_1^TE_1^T + \bar x_2^TE_2^T - \xi b^T,\; \bar x_1^T
                )
                \\
                &= 
                (
                    E_1^T\bar y + \xi c_1, \;
                    E_2^T \bar y + \xi c_2, \;
                    E_1\bar x_1 + E_2\bar x_2 - \xi b, \;
                    \bar x_1
                )^T. 
            \end{align*}
            \begin{enumerate}
                \item Two multiplications of $E$: $\bar y$ on the left and for $\bar x_1, \bar x_2$ on the right, 
                \item one vector addition with $c = (c_1, c_2)$ and $b$. 
            \end{enumerate}
            Therefore, computing $A^TAv$ has four vector multiplications using $E$. 
            In practice, a sparse matrix $E$ from the model can speed up computations. 
            \par
            Another key operation would be $A^TAv$. 
            Let $\bar v = Av$, then 
            \begin{align*}
                A^TAv &= 
                \begin{bmatrix}
                    E^T_1(E_1x_1 + E_2x_2) + (c_1^Tx_1 + c_2^Tx_2 - b^Ty)c_1
                    \\
                    E^T_2(E_1x_1 + E_2x_2) + (c_1^Tx_1 + c_2^Tx_2 - b^Ty)c_2
                    \\
                    E_1(E_1^Ty + z) + E_2E_2^Ty - (c_1^Tx_1 + c_2^Tx_2 - b^Ty)b
                    \\
                    E_1^Ty + z
                \end{bmatrix}
                \\
                &= 
                \begin{bmatrix}
                    (E_1^TE_1 + c_1^T)x_1 + (E_1^TE_2 + c_2^T)x_2 - (c_1b^T)y
                    \\
                    (E_2^TE_1 + c_1^T)x_1 + (E_2^TE_2 + c_2^T)x_2 - (c_2b^T)y
                    \\
                    -(bc_1^T)x_1 - (bc_2^T)x_2 + (E_2E_2^T + E_1E_1^T + bb^T)y
                    + (E_1E_1^T)z
                    \\
                    E_1^Ty + z
                \end{bmatrix}. 
            \end{align*}
            In practice, implicitly representing the process of $A^TAv$ is better in computing software. 
            Here we write it out to view, for theoretical interests. 
            \par
            Let $f(v) = (1/2)\Vert Av - d\Vert^2$ to be the objective function of optimization problem \eqref{problem:lp-kkt-min}. 
            Its gradient, objective value, and Bregman Divergence have: 
            \begin{align*}
                \nabla f(v) &= A^TAv - A^Td, 
                \\
                f(v) &= 
                \frac{1}{2}\langle v, \nabla f(v) - A^Td\rangle + \frac{1}{2}\Vert d\Vert^2, 
                \\
                D_f(u, v) &= (1/2)\langle u - v, A^TA (u - v)\rangle
                \\
                &= (1/2)\langle \nabla f(u) - \nabla f(v), u - v\rangle. 
            \end{align*}
            The value $\nabla f(v), f(v)$ when evaluated together, require minimal additional computations. 
            This fact is favorable for implementations in practice. 
            Furthermore, the difference of the function value between 2 points $v, u$ admits an interesting relation via the Bregman Divergence. 
            Observe that $\forall u, v \in \RR^n$ it has 
            \begin{align*}
                f(u) - f(v) &= \langle \nabla f(v), u - v \rangle + D_f(u, v)
                \\
                &= \langle \nabla f(v), u - v \rangle + (1/2)\langle \nabla f(u) - \nabla f(v), u - v\rangle
                \\
                &= (1/2)\langle \nabla f(u) + \nabla f(v), u - v\rangle. 
            \end{align*}
            For this problem, the computation overhead for $f(u) - f(v), D_f(u, v)$ is very little if $\nabla f(u), \nabla f(v)$ is known.

@@

                (1 - \alpha_k)(F(x_{k - 1}) - F(x^+)) + \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_k\Vert^2

@@

                \frac{L_{k - 1}\alpha_{k - 1}^2(\rho_{k - 1}L_kL_{k - 1}^{-1})}{2}\Vert x^+ - v_k\Vert^2 \\

@@

                    \Vert x^+ - v_k\Vert^2

>>>>

@@

@@

            Let $\bar v = (\bar y, \bar x_1, \bar x_2, \xi) \in \RR^m\times \RR^{n_1} \times \RR^{n_2}\times \RR$ then the right multiplication of has: 
                \bar v^TA  &= (
                    E_1^T\bar y + \xi c_1^T,\; E_2^T\bar y + \xi c_2^T,\; 
                    \bar x_1^TE_1^T + \bar x_2^TE_2^T - \xi b^T,\; \bar x_1^T
                )
                (
                    E_1^T\bar y + \xi c_1, \;
                    E_2^T \bar y + \xi c_2, \;
                    E_1\bar x_1 + E_2\bar x_2 - \xi b, \;
                    \bar x_1
                )^T. 
                \item Two multiplications of $E$: $\bar y$ on the left and for $\bar x_1, \bar x_2$ on the right, 
                \item one vector addition with $c = (c_1, c_2)$ and $b$. 
            Therefore, computing $A^TAv$ has four vector multiplications using $E$. 
            In practice, a sparse matrix $E$ from the model can speed up computations. 
            Another key operation would be $A^TAv$. 
            Let $\bar v = Av$, then 
                A^TAv &= 
                    E^T_1(E_1x_1 + E_2x_2) + (c_1^Tx_1 + c_2^Tx_2 - b^Ty)c_1
                    E^T_2(E_1x_1 + E_2x_2) + (c_1^Tx_1 + c_2^Tx_2 - b^Ty)c_2
                    E_1(E_1^Ty + z) + E_2E_2^Ty - (c_1^Tx_1 + c_2^Tx_2 - b^Ty)b
                    E_1^Ty + z
                \end{bmatrix}
                    (E_1^TE_1 + c_1^T)x_1 + (E_1^TE_2 + c_2^T)x_2 - (c_1b^T)y
                    (E_2^TE_1 + c_1^T)x_1 + (E_2^TE_2 + c_2^T)x_2 - (c_2b^T)y
                    -(bc_1^T)x_1 - (bc_2^T)x_2 + (E_2E_2^T + E_1E_1^T + bb^T)y
                    + (E_1E_1^T)z
                    E_1^Ty + z
                \end{bmatrix}
                    E_1^TE_1 + c_1^T & E_1^TE_2 + c_2^T & -c_1b^T & \\
                    E_2^TE_1 + c_1^T & E_2^TE_2 + c_2^T & -c_2b^T & \\
                    -bc_1^T& -bc_2^T & E_2E_2^T + E_1E_1^T + bb^T & E_1E_1^T \\
                    & & & E_1^Ty + z\\
                \end{bmatrix}
                    x_1 \\ x_2 \\ y \\ z
            In practice, implicitly representing the process of $A^TAv$ is better in computing software. 
            Here we write it out to view, for theoretical interests. 
            Let $f(v) = (1/2)\Vert Av - d\Vert^2$ to be the objective function of optimization problem \eqref{problem:lp-kkt-min}. 
            Its gradient, objective value, and Bregman Divergence have: 
                \nabla f(v) &= A^TAv - A^Td, 
                f(v) &= 
                \frac{1}{2}\langle v, \nabla f(v) - A^Td\rangle + \frac{1}{2}\Vert d\Vert^2, 
                D_f(u, v) &= (1/2)\langle u - v, A^TA (u - v)\rangle
                &= (1/2)\langle \nabla f(u) - \nabla f(v), u - v\rangle. 
            The value $\nabla f(v), f(v)$ when evaluated together, require minimal additional computations. 
            This fact is favorable for implementations in practice. 
            Furthermore, the difference of the function value between 2 points $v, u$ admits an interesting relation via the Bregman Divergence. 
            Observe that $\forall u, v \in \RR^n$ it has 
                f(u) - f(v) &= \langle \nabla f(v), u - v \rangle + D_f(u, v)
                &= \langle \nabla f(v), u - v \rangle + (1/2)\langle \nabla f(u) - \nabla f(v), u - v\rangle
                &= (1/2)\langle \nabla f(u) + \nabla f(v), u - v\rangle. 
            For this problem, the computation overhead for $f(u) - f(v), D_f(u, v)$ is very little if $\nabla f(u), \nabla f(v)$ is known.

@@

                (1 - \alpha_k)(F(x_{k - 1}) - F(x^+)) + \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_{k - 1}\Vert^2

@@

                \frac{L_{k - 1}\alpha_{k - 1}^2(\rho_{k - 1}L_kL_{k - 1}^{-1})}{2}\Vert x^+ - v_{k-1}\Vert^2 \\

@@

                    \Vert x^+ - v_{k - 1}\Vert^2

### 2025-04-30 Notebook LaTEX/R-WAPG/presentation.tex
>w<, changes

\section{This is the First Section}
    \subsection{Taxonomy of Proximal type of Methods}
        \begin{frame}{Frame Title}

            \begin{block}{Formula Presented in Block}
                \begin{align}
                    \min_{x} g(x) + h(x)
                \end{align}    
            \end{block}

            \begin{itemize}
                \item [1.]Throughout this presentation, we assume the objective of a function $f$ is the sum of 2 functions.
                \item [2.]We are interested in the paper: FISTA (Fast Iterative-Shrinkage Algorithm) by Beck and Teboulle \cite{paper:FISTA}. 
                \pause 
                \item [1.] When $h = \delta_Q$ with $Q$ closed and convex with $Q\subseteq \text{ri}\circ \text{dom}(g)$, we use projected subgradient. 
                \item [2.] When $g$ is \textbf{\emph{strongly smooth}} and $h$ is \textbf{closed convex proper} whose proximal oracle is easy to compute, we consider the use of FISTA. 
            \end{itemize}

@@

    \subsection{The Proximal Operator}
        \begin{frame}{Frame Title}
            \begin{definition}[Definition of Something]
                Let $f$ be convex closed and proper, then the proximal operator parameterized by $\alpha > 0$ is a non-expansive mapping defined as: 
                \begin{align*}
                    \text{prox}_{f, \alpha}(x) := 
                    \arg\min_{y}\left\lbrace
                        f(y) + \frac{1}{2\alpha} \Vert y - x\Vert^2
                    \right\rbrace. 
                \end{align*}
            \end{definition}  
            \begin{remark}
                When $f$ is convex, closed, and proper, 
            \end{remark}
        \end{frame}

        \begin{frame}{Prox is the Resolvant of Subgradient}
            \begin{lemma}[The Lemma]\label{lemma:prox_alternative_form}
                When the function $f$ is convex closed and proper, the $\text{prox}_{\alpha, f}$ can be viewed as the following operator $(I + \alpha \partial f)^{-1}$. 
            \end{lemma}
            \begin{proof}
                Minimizer satisfies zero subgradient condition, 
                {\scriptsize
                \begin{align*}
                    \mathbf 0 &\in \partial
                    \left[
                        \left.
                            f(y) + \frac{1}{2\alpha} \Vert y - x\Vert^2 
                        \right| y
                    \right](y^+)
                    \\
                    \mathbf 0 &\in \partial f(y^+) + \frac{1}{\alpha}(y^+ - x)
                    \\
                    \frac{x}{\alpha} &\in 
                    (\partial f + \alpha^{-1}I)(y^+)
                    \\
                    x &\in 
                    (\alpha \partial f + I)(y^+)
                    \\
                    y &\in (\alpha\partial f+ I)^{-1}(x).
                \end{align*}
                }
            \end{proof}

    \subsection{Strong Smoothness}
        \begin{frame}{Equivalence of Strong Smoothness and Lipschitz Gradient}
            \begin{theorem}[Lipschitz Gradient Equivalence under Convexity]
                Suppose $g$ is differentiable on the entire of $\mathbb E$. It is closed convex proper. It is strongly smooth with parameter $\alpha$ if and only if the gradient $\nabla g$ is globally Lipschitz continuous with a parameter of $\alpha$ and $g$ is closed and convex. 
                \begin{align*}
                    \Vert \nabla g(x) -\nabla g(y)\Vert \le 
                    \alpha 
                    \Vert x - y \Vert\quad \forall x, y\in \mathbb E
                \end{align*}
            \end{theorem}
            \begin{proof}
                Using line integral, we can prove Lipschitz gradient implies strong smoothness without convexity. The converse requires convexity and applying generalized Cauchy Inequality to (iv) in Theorem 5.8 for Beck's textbook \cite{book:first_order_opt}. 
            \end{proof}

        \end{frame}
    \subsection{A Major Assumption}    
        \begin{frame}{A Major Assumption}
            \begin{assumption}[Convex Smooth Nonsmooth with Bounded Minimizers]\label{assumption:1}
                We will assume that $g:\mathbb E\mapsto \mathbb R$ is \textbf{strongly smooth} with constant $L_g$ and $h:\mathbb E \mapsto \bar{\mathbb R}$ \textbf{is closed convex and proper}. We define $f := g + h$ to be the summed function and $\text{ri}\circ \text{dom}(g) \cap \text{ri}\circ \text{dom}(h) \neq \emptyset$. We also assume that a set of minimizers exists for the function $f$ and that the set is bounded. Denote the minimizer using $\bar x$. 
            \end{assumption}
        \end{frame}

\section{A New Fancy Section}
    \subsection{A Fancy Subsetction for Algorithm}
        \begin{frame}{The Accelerated Proximal Gradient Method}
            \begin{block}{Momentum Template Method}
                \begin{algorithm}[H]
                    \begin{algorithmic}[1]
                        \STATE{\textbf{Input:} $x^{(0)}, x^{(-1)}, L, h, g$; 2 initial guesses and stepsize L}
                        \STATE{$y^{(0)} = x^{(0)} + \theta_k (x^{(0)} - x^{(-1)})$}
                        \FOR{$k = 1, \cdots, N$}
                            \STATE{$x^{(k)} = \text{prox}_{h, L^{-1}}(y^{(k)} + L^{-1}\nabla g(y^{(k)})) =: \mathcal P_{L^{-1}}^{g, h}(y^{(k)})$}
                            \STATE{$y^{(k + 1)} = x^{(k)} + \theta_k(x^{(k)} - x^{(k - 1)})$}
                        \ENDFOR
                    \end{algorithmic}
                    \caption{Template Proximal Gradient Method With Momentum}\label{alg:fista_template}
                \end{algorithm}
            \end{block}
        \end{frame}

\section{Numerical Experiments}
    \input{Sections/sectionfile.tex}

>>>>

\section{This is the First Section}
    \subsection{Taxonomy of Proximal type of Methods}
        \begin{frame}{Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations}

@@
